Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

\section{Introduction}
% Modified from project proposal

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data set}

@@

Users are able to filter messages by age, sex, continent and country. At this time,

@@

At the beginning of this research project, slightly two million messages had been flagged by moderators as spam. We extracted the contents of exactly two million spam-labeled messages from accounts deleted by moderators between October 2011 and March 2012. As moderators can flag a user's entire list of outgoing messages as spam on deletion, the earliest sent dates of some messages in our data set begin in May 2010.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

@@

%classification:
%- implemented 3 models: naive bayes, linear regression, and SVM.
%- used scalanlp for naive bayes
%- used matlab for linear regression with ridge regularization.

@@

%We use a na\``ive Bayes model, in which the documents are generated according to the following process.  
%First, a class \(c\) is chosen from a probability distribution \(\Pr(c)\).
%Then, a document from class \(c\) is generated.
%We tried a multinomial model and a Bernoulli model to model this process.
%\begin{itemize}
%\item \emph{Multinomial model.}  A document length \(m_d\) is chosen and \(m_d\) words \(w_{d,1}, \dotsc, w_{d,m_d}\) are chosen independently from a distribution \(\Pr(w|c)\).
%\item \emph{Bernoulli model.}  For each word \(w\) in the vocabulary, \(w\) is added to the document with probability \(\Pr(w|c)\).
%\end{itemize}
%The distributions \(\Pr(c)\) and \(\Pr(w|c)\) are parameters of the model.
%
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

>>>>

\section{Introduction}

@@

\section{Related Work}

@@

\section{Data set}

@@

%- Users are able to filter messages by age, sex, continent and country. At this time, 
%- Duplicate account detection

@@

At the beginning of this research project, slightly two million messages had 
been flagged by moderators as spam. We extracted the contents of exactly 2 million 
spam-labeled messages from accounts deleted by moderators between October 2011 
and March 2012. As moderators can flag a user's entire list of outgoing messages 
as spam on deletion, the earliest sent dates of some messages in our data set begin in 
May 2010.

@@

\section{Methodology}

@@

@@

@@

\section{Future Work}

@@

\section{Conclusion}
